Paper

### 2021-10-12 draft_paper.Rmd
updating paper draft

# read in forecasts
# path to UoM server different for everyone
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")

@@

  # conditionally label y axis
  y_axis_label <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast", 
                                           "domestic_by_grade_rt_forecast", 
                                           "domestic_by_grade_volume_forecasts") ~ "Median response time (in minutes)", 
                         df_name %in% c("call_forecasts") ~ "Weekly count of calls for service", 
                         df_name %in% c("by_type_attended_forecast", "by_grade_attended_forecast") ~ "Weekly % of calls attended")

  # conditionally find actual value column
  actual_col_name <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast",
                                           "domestic_by_grade_rt_forecast", 
                                           "domestic_by_grade_volume_forecasts") ~ "actual_rt", 
                         df_name %in% c("call_forecasts") ~ "actual_calls", 
                         df_name %in% c("by_type_attended_forecast",
                                        "by_grade_attended_forecast") ~ "actual_attended")

@@

However when we break down by grade of call

@@

forecast_chart(domestic_by_grade_rt_forecast,"initial_grade_of_response", "Grade 1")

@@

@@

# Attended by grade fig

@@

Police response by grade. For grade 1, response time was within what was forecasted, however for grade 2 calls response times decreased during the pandemic. For grades 3 and 4 the forecase is too noisy (too few observations).

>>>>

# read in forecasts
# path to UoM server different for everyone
call_forecasts <- read_rds("/Volumes/n8_covid/call_forecasts.Rds")
all_rt_forecast <- read_rds("/Volumes/n8_covid/all_resp_time_forecast.Rds")
by_type_rt_forecast <- read_rds("/Volumes/n8_covid/by_type_rt_forecasts.Rds")
by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/by_grade_rt_forecasts.Rds")
all_calls_attended_forecast <- read_rds("/Volumes/n8_covid/all_attended_forecasts.Rds")
by_type_attended_forecast <- read_rds("/Volumes/n8_covid/by_type_attended_forecasts.Rds")
domestic_by_grade_volume_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_volume_forecasts.Rds")
domestic_by_grade_rt_forecast <- read_rds("/Volumes/n8_covid/domestic_by_grade_rt_forecasts.Rds")
domestic_by_grade_attended_forecasts <- read_rds("/Volumes/n8_covid/domestic_by_grade_attended_forecasts.Rds")

@@

  # conditionally label y axis
  y_axis_label <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast", 
                                           "domestic_by_grade_rt_forecast") ~ "Median response time (in minutes)", 
                         df_name %in% c("call_forecasts", 
                                           "domestic_by_grade_volume_forecasts") ~ "Weekly count of calls for service", 
                         df_name %in% c("by_type_attended_forecast",
                                        "by_grade_attended_forecast", 
                                        "domestic_by_grade_attended_forecasts") ~ "Weekly % of calls attended")

  # conditionally find actual value column
  actual_col_name <- case_when(df_name %in% c("by_type_rt_forecast", 
                                           "by_grade_rt_forecast",
                                           "domestic_by_grade_rt_forecast") ~ "actual_rt", 
                         df_name %in% c("call_forecasts", 
                                           "domestic_by_grade_volume_forecasts") ~ "actual_calls", 
                         df_name %in% c("by_type_attended_forecast",
                                        "by_grade_attended_forecast", 
                                        "domestic_by_grade_attended_forecasts") ~ "actual_attended")

@@

This does not change when we break down by grade of call.

@@

forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 1")
forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 2")
forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 3")
forecast_chart(domestic_by_grade_volume_forecasts,"initial_grade_of_response", "Grade 4")

@@

However we do see an increased response from police to Domestic Incident calls. Not so much for grade 1, which were attended near 100% of cases before, during, and after the pandemic, but for calls initially graded as grade 2 attendance rate increased. Grade 3 and 4 are again too noisy for anything.

@@

# Attended by grade fig
forecast_chart(domestic_by_grade_attended_forecasts,"initial_grade_of_response", "Grade 1")
forecast_chart(domestic_by_grade_attended_forecasts,"initial_grade_of_response", "Grade 2")

@@

In fact, as well as responding to more calls initially graded as grade 2, response time to these calls has decreased as well. While response time for grade 1 calls was within what was forecasted, for grade 2 calls response times decreased during the pandemic. (for grades 3 and 4 the forecast is too noisy).
